---
title: "genealogy"
output: html_document
---

original setup
```{r, echo = FALSE, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.height = 4,
  fig.width = 8,
  fig.align = "center",
  cache = FALSE
)
library(ggplot2)
library(tidyr)
library(dplyr)
library(lubridate)
library(scales)
library(readr)
library(ggmap)
library(RColorBrewer)
library(gridExtra)
library(ggenealogy)
```

## overall function--> study pedigree

- `pedigree`: standardized chart used to study human family lines (Coster, 2013)
- `kinship2`: basic pedigree charts (Therneau, Daniel, Sinnwell, Atkinson, 2015)
- `ggenealogy`: focused on agronomic genealogical lineages (Rutter, Vanderplas, Cook, Graham 2016)

#example 1--soybean
```{r}
data("sbGeneal")
str(sbGeneal)
```

STEP1: Conversion to graph structure
```{r}
sbIG <- dfToIG(sbGeneal)
sbIG
```

STEP2: get basic statistic 
```{r}
getBasicStatistics(sbIG)
```

STEP3: Apply some functions

- shortest path
- plotting ancestors and descendants
- plotting distance matrix
- using interaction

# function1: get shortest path (getPath and plotPath)
```{r fig.show='hide'}
pathTN <- getPath("Tokyo", "Narow", sbIG, sbGeneal)
pathTN
plotPath(pathTN)
```

note: plot path for all(the plot is messy)
```{r}
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol =
  "seagreen2", nodeSize = 1, pathNodeSize = 3)
```

#function2: plotting ancestors and descendants(use plotAncDes function)
```{r}
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
```

#function3: plotting distance matrix(use plotdegmatrix to draw a heatmap)
```{r fig.show='hide'}
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow",
  "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, 
              "Variety", "Variety", "Degree") +
  ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") +
  ggplot2::theme(legend.title = ggplot2::element_text(size = 15),
                 legend.text
  = ggplot2::element_text(size = 15))
```

#function4: plot interactions(use a package plotly)
```{r eval=FALSE}
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, 
              pathEdgeCol = "seagreen2", nodeSize = 1, 
              pathNodeSize = 3,
   animate = TRUE)
```

#Part2: how to plot a networks(use geom_net)

orignial setup
```{r}
install.packages("geomnet")
library(geomnet)
data(blood)
head(blood$edges, 3)
head(blood$vertices, 3)
bloodnet <- left_join(blood$edges, blood$vertices, by=c("from" = "label"))
```

note: plot the direct network of blook donation

```{r}
p <- ggplot(data = bloodnet, aes(from_id = from, to_id = to))
p %>% geom_net(label = TRUE, size = 15, labelcolour="white", vjust=0.5, hjust=0.5, directed=TRUE, arrowgap=0.075) %>% theme_net()
```


