---
title: "interactive_plot"
output: html_document
---
original setup
```{r echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.height = 4,
  fig.width = 8,
  fig.align = "center",
  cache = FALSE
)
```
```{r echo=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(lubridate)
library(scales)
library(readr)
library(ggmap)
library(HLMdiag)
library(RColorBrewer)
library(gridExtra)
library(plotly)
library(ggvis)
```

##Part1: ggvis
```{r}
library(ggvis)
data("economics", package = "ggplot2")

ggvis(economics, x=~date, y=~psavert)
```

```{r}
economics %>%
  ggvis(~date, ~psavert) %>%
  layer_points() %>%
  layer_smooths()
```

#make the graph dynamic viewing(use label_smooth function)
(the input does not need to be static, you can change it and see the dynamic)
```{r}
economics %>%
  ggvis(~date, ~psavert) %>%
  layer_points() %>%
  layer_smooths(
    span = input_slider(0.2, 1),
    stroke := "red"
    #when you change color, need to use stroke and a sepcific character
  )
```

#make dynamic label
```{r}
economics %>%
  ggvis(~date, ~psavert) %>%
  layer_points() %>%
  layer_smooths(
    span = input_slider(0.2, 1)
  )
```

#use a checkbox to switch from linear regression model and the slider function
```{r eval=FALSE}
model_type <- input_checkbox(label = "Use loess curve",
  map = function(val) if(val) "loess" else "lm")
economics %>%
  ggvis(~date, ~psavert) %>%
  layer_points() %>%
    layer_model_predictions(model = model_type)
```

#add three button choice(lm or loess or radio button)
```{r eval=FALSE}
model_type <- input_radiobuttons(
  choice = c("linear" = "lm", 
             "LOESS" = "loess", 
             "Robust" = "rlm"), 
              selected = "loess",
              label = "Model type")
economics %>%
  ggvis(~date, ~psavert) %>%
  layer_points() %>%
  add_tooltip(all_values, "hover") %>%
    layer_model_predictions(model = model_type)
```

# Part2 Add interactive elements to ggplots using plotly

# add the label
```{r eval=FALSE}
library(plotly)
plot_ly(economics, x = date, y = unemploy / pop)
```

# add the label using ggplot2
```{r}
ggplot(data=economics, aes(x = date, y = unemploy / pop)) +  
        geom_point() + geom_line()
```

```{r}
ggplotly()
```

#use ggally to get pairs of dynamic graph(ggpairs first and then use ggplotly)
```{r}
library(GGally)
p <- ggpairs(economics[,3:6])
ggplotly(p)
```

#make a map
```{r}
data(canada.cities, package = "maps")
viz <- ggplot(canada.cities, aes(long, lat)) +
  borders(regions = "canada") +
  coord_equal() +
  geom_point(aes(text = name, size = pop), colour = "red", alpha = 1/2)
 ggplotly(viz)
```

# Part3 use interactive plot to analyze RNA-seq data

original setup
```{r echo=FALSE}
library(edgeR)
coty <- read_delim("~/Desktop/SISBID-2016-master/data/GSE61857_Cotyledon_normalized.txt.gz",
  delim="\t", col_types="cddddddddd", 
  col_names=c("ID", "C_S1_R1", "C_S1_R2", "C_S1_R3", 
  "C_S2_R1", "C_S2_R2", "C_S2_R3", "C_S3_R1", "C_S3_R2", "C_S3_R3"),
  skip=1)
coty <- as.data.frame(coty)
d <- DGEList(counts = coty[,2:7], 
  group = c(rep("S1", 3), rep("S2", 3)), 
  genes = coty[,1])
d <- calcNormFactors(d)
d <- estimateCommonDisp(d)
d <- estimateTagwiseDisp(d)
d <- estimateTrendedDisp(d)
de <- exactTest(d, pair=c("S1", "S2"), dispersion = "trended")
sig.tab <- de$table
sig.tab$genes <- coty$ID
sig.tab <- dplyr::filter(sig.tab, PValue < 0.01)
sig.tab <- merge(sig.tab, coty[,1:7], by.x="genes", by.y="ID")
ggscatmat(sig.tab, columns=5:10, alpha=0.1)
```

# dynamic label a specific gene in the graph
```{r fig.width=4, fig.height=4}
p <- ggplot(sig.tab, aes(x=C_S1_R2, y=C_S2_R1, label=genes)) +
  geom_point(alpha=0.1) 
ggplotly(p)
```
note: so when we show this in the presentation, we can see dot directly. then we can extract the information and plot a interactive plot.

#anothe example
all plots here are made in ggblot2; just make it into interactive preface.
```{r eval=FALSE}
install.packages("eechidna")
library(eechidna)
launchApp(
  age = c("Age20_24", "Age85plus"),
  religion = c("Christianity", "Catholic", "NoReligion"),
  other = c("Unemployed", "Population", "MedianIncome")
)
```
